---
#title: "Burlington Police Incidents"
#author: "Jane Adams, RJ Luongo, Reed Simon"
#date: "10/28/2019"
output: html_document
---

# Burlington Police Incidents

> Through October 1, 2019

Jane Adams, RJ Luongo, Reed Simon

# Data Cleaning

Importing police incidents and loading required packages

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

i <- read.csv("./Incidents_2019-10-01.csv")
library(tidyverse)
library(lubridate)
```

First we, use luridate to format the call date and time in a way that's easier to analyze and plot.

```{r cleani}
i <- i %>% 
  mutate(DayOfWeek = lubridate::wday(call_time, label = TRUE)) %>% 
  mutate(Hour = lubridate::hour(call_time)) %>% 
  mutate(Month = lubridate::month(call_time, label = TRUE)) %>% 
  mutate(DayOfMonth = lubridate::day(call_time))
```

We then remove the columns that aren't relevant to our analysis and bloat the dataset.

```{r removecol}
i <- i %>% select(-c(incident_number, call_time, Street, call_origin, Area, Latitude, Longitude))
```

Here we plot the total number of incidents for each day of the week.

```{r exampleplot}
ggplot(data = i, mapping = aes(x = DayOfWeek)) + geom_bar() +
  theme_bw() + theme(axis.text.x = element_text(hjust=1, angle = 45)) +
  labs(title = "Total Count of Incidents by Day of Week", y = "Count", x = "Day of Week")
```

And here we look at the distribution of type of incident for each day of the week.

```{r incidentbytype}
ggplot(data = i, mapping = aes(x = DayOfWeek, fill = call_type_group)) + 
  geom_bar(position = 'fill') +
  theme_bw() + theme(axis.text.x = element_text(hjust=1, angle = 45)) +
  labs(title = "Incidents by Day of Week, Grouped by Incident Type")
```

